Verifying Demonstrations

### 2018-02-28 paper/LocationProofs.tex
Changes "\emph{e.g.}," to "\eg" and "\emph{i.e.}," to "\ie"

Some Location-Based Services (\emph{LBS}) only grant access to resources to users located at a particular location,  thus raising the issue of verifying the position claimed by a particular user. 
In most current schemes, the location of a user/device is determined by the device itself (\emph{e.g.}, through GPS) and forwarded to the LBS provider. 
One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

To counter this threat, a LBS should ask the requesting device to formally prove that it really is at the claimed location. This notion can be formalized through the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\emph{e.g.}, trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof. 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
%Seb: to do add the corresponding reference
However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\emph{i.e.}, crowd estimation) in contrast to checking the location claim made a user, which is an individual property.

>>>>

Some Location-Based Services (\emph{LBS}) only grant access to resources to users located at a particular location,  thus raising the issue of verifying the position claimed by a particular user. 
In most current schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the LBS provider. 
One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

To counter this threat, a LBS should ask the requesting device to formally prove that it really is at the claimed location. This notion can be formalized through the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof. 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
%Seb: to do add the corresponding reference
However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made a user, which is an individual property.

### 2018-02-28 paper/SystemModel.tex
Changes "\emph{e.g.}," to "\eg" and "\emph{i.e.}," to "\ie"

\emph{Formalizing the notion of crowd estimation.} Each participant who wants to be counted must submit a participation proof.
The proof must be associated with the protest (\emph{i.e.}, its identifier \(cid\)), time and location must coincide with any of its subprotests.

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}
The strength function \(s\) can be used to regulate trust in witnesses.
One example would be for \(s\) to return the number of proof shares (\emph{i.e.}, witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.

>>>>

\emph{Formalizing the notion of crowd estimation.} Each participant who wants to be counted must submit a participation proof.
The proof must be associated with the protest (\ie its identifier \(cid\)), time and location must coincide with any of its subprotests.

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}
The strength function \(s\) can be used to regulate trust in witnesses.
One example would be for \(s\) to return the number of proof shares (\ie witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.

### 2018-02-28 paper/intro.tex
Changes "\emph{e.g.}," to "\eg" and "\emph{i.e.}," to "\ie"

Existing methods for crowd-counting varies significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
However, most of them lack precision (\emph{i.e.}, they have large error margins) and they can only give an estimate for a particular snapshot in time (\emph{e.g.}, at the peak of the event). 
In particular, the existing methods cannot estimate reliably the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they also lack verifiability as everyone has to trust the entity responsible for performing the counting.
Finally, one important observation about crowd-counting that has been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting.

Indeed, going back to our example Alice the activist has an incentive to increase the tallied number of participants, whereas Eve (and possibly other entities) have an incentive to decrease the tallied number of participants.
In this case, we are left with two options: either we trust Alice or Eve or we have to be able to verify their claims.
In this paper, our main objective is to provide a scheme preventing both Alice and Eve from cheating (\emph{i.e.}, their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist to Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent a physical eavesdropper from recognizing a particular individual in a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated to his identity and that his actions are also unlinkable.

%Seb: I suggest that we move this part to system model
%\subsection{Combining properties of electronic voting with location proofs}
\emph{Relationship between protesting and electronic voting}. In general, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
These opinions can be sensitive (\emph{e.g.}, be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility]: anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability]: anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability]: every voter can verify that their vote is included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\emph{i.e.}, each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
We will define these more formally in \cref{Verifiability}.

@@

However, we believe that some assumptions might become sufficiently realistic in the near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\emph{e.g.}, Estonia and Germany)
In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available can already enable proofs of proximity with a range of 200 meters.
One of the short-term objective is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.

>>>>

Existing methods for crowd-counting varies significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot estimate reliably the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
In addition, they also lack verifiability as everyone has to trust the entity responsible for performing the counting.
Finally, one important observation about crowd-counting that has been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting.

Indeed, going back to our example Alice the activist has an incentive to increase the tallied number of participants, whereas Eve (and possibly other entities) have an incentive to decrease the tallied number of participants.
In this case, we are left with two options: either we trust Alice or Eve or we have to be able to verify their claims.
In this paper, our main objective is to provide a scheme preventing both Alice and Eve from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist to Sybil attacks while still preserving the participants'
privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent a physical eavesdropper from recognizing a particular individual in a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated to his identity and that his actions are also unlinkable.

%Seb: I suggest that we move this part to system model
%\subsection{Combining properties of electronic voting with location proofs}
\emph{Relationship between protesting and electronic voting}. In general, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility]: anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability]: anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability]: every voter can verify that their vote is included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
We will define these more formally in \cref{Verifiability}.

@@

However, we believe that some assumptions might become sufficiently realistic in the near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\eg Estonia and Germany)
In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available can already enable proofs of proximity with a range of 200 meters.
One of the short-term objective is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.
